%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\footskip}{4.09pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Boussejra Amir}} & Email : \href{mailto:amir@boussejra.com}{amir@boussejra.com}\\ \textbf{\textit{Software/Machine Learning/Data Engineer}}, 42000 Saint-Etienne & Mobile : \href{tel:+33619147668}{+33619147668} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ecole des Mines de Saint-Etienne}{Saint-Etienne, France}
      {Master's degree in Computer Science and Data Science}{Sep. 2019 -- Sep. 2022}
    \resumeSubheading
      {University Lyon 1}{Lyon, France}
      {Master's degree in Applied Mathematics (Dual Degree with Ecole des Mines)}{Sep. 2020 -- Sep. 2022}
    \resumeSubheading
      {MPSI/MP*, Lycée Carnot}{Dijon, France}
      {Preparation for national competitive entrance exams leading to top French Engi-neering Schools}{Sep. 2017 -- Sep. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Viavi Solutions}{Saint-Etienne, France}
      {Embedded ML Software Engineer}{Dec 2022 - Present}
      \resumeItemListStart
      \resumeItem{Data-Driven custom ML improvements}
        { MLOPS monitored solution for automating retraining pipelines on client's annotated data to continuously improve measurement algorithms.
        \\Federated Learning for CI of base models.
        \\ \textbf{Result:} Developed retraining/qualification pipelines to assess CI of models, linked with MLFlow server to monitor models.
        Managed project to get ability to connect to client's proprietaty cloud (managed by Viavi US) to retrieve client's data, 
        created dedicated docker envs to train on on-premise servers client specific models and push back updated models to cloud (syncs with embedded platforms when network is available).}
        \resumeItem{Detection of Fiber Faults in OTDR Traces}
          {Optical Time Domain Reflectometer (OTDR) traces analysis using ML. Design and Implementation of data pipelines to go from proprietary format (.sor) to ML exploitable data and embedded ML models. Introduction of CI/CD and MLOps principles for embedded ML project.
          \\ \textbf{Result:} Successful integration between high-level ML models, data pipelines in Python and storage in SQL to trace ML algorithm performances. To exploitation on embedded devices using ONNX models and software/hardware optimization on resource-constrained devices (CPU-bound) and leveraging those new algorithms alongside legacy software to keep overall functionality intact.}
      \resumeItem{Agile Software Development for Short-Term Projects}
        {
          \begin{enumerate}
            \item \textbf{Bugfixing for Major Releases:} Twice a year a major release is issued, and all efforts are into treating found bugs. Being bugs found by PLM/Client/Engineer. Mostly debugging complex algorithmic code that require gdb skills. 
            \item \textbf{Tooling deployment:} Deploy custom local PyPi, DockerHub servers to favor intra-engineer package sharing. Automated tests writing linked with Jenkins server.
            \item \textbf{CI/CD of Signal Processing Algorithms:} Developed an R\&D tool to automatically assess performance changes in signal processing algorithms using a dedicated mySQL database. Resulted in improved efficiency and reliability of signal processing systems by automating statistical performance measurements on client reference curves, ensuring global improvements with each development iteration.
            \item \textbf{Library for custom files output:} Created dynamic library for a client use case to convert our propietary formats to json reports complying with their DB schema.
            \item \textbf{Fire Detection with Distributed Temperature Sensors:} Leveraged the Raman effect to correlate fiber trace to temperature, enabling gradient monitoring over time for early diagnosis of fire starts. Successfully integrated this solution for Siemens' final client, incorporating gradient monitoring and custom setups to send alarms to their servers.
          \end{enumerate}
        }
      \resumeItemListEnd

% --------Multiple Positions Heading------------ Same company
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Epigno Corporation}{Tokyo, Japan}
      {Part Time Full-Stack Software Engineer}{Dec 2022 - Present}
      \resumeItemListStart
       \resumeItem{Continuous improvement of doctor's schedule optimization program}
         {With evolving client's demands and some new doctor's work law rising, there is a need for continuous improvement.
         \\\textbf{Result:} (Rust only) Development of new logic, heuristics or specification changes needs relative to hospital's priority and law regulations policies.}
      \resumeItemListEnd
      \pagebreak
   \resumeSubSubheading
      {Full Time Full-Stack Software Engineer}{Oct 2022 - Dec 2022}
      \resumeItemListStart
       \resumeItem{Integration in global app of doctor's schedule optimization program}
         {Serving the optimizer as a deployed Microservice in an EC2 instance on AWS, definition of APIs to communicate between Frontend in Vue3/TS, backend in PHP/Laravel, DB in MySQL and Rust optimizer. Development of websocket client/server to get gradual results returned to frontend and UI development to display results working with designer's advices.
         \\\textbf{Result:} Working webapp in production for first sales. (Backend/DB/Frontend integration of optimizer's API)}
      \resumeItemListEnd
   \resumeSubSubheading
    {Part Time Optimization Engineer and Software Engineer}{Sep 2021 - Sep 2022}
    \resumeItemListStart
       \resumeItem{Doctor's schedule optimization program}
         {Rust development of a program for doctor's shift automatic allocation corresponding to their skills, needs, demands and law regulations, merging with a nurse shift allocation program to make a general hospital staff shift problem solver.
         \\\textbf{Result:} MVP that works as intended on example database from Kanto's Hospital.}
       \resumeItem{Devops General Work}
         {Upgrade a codebase's frontend from Node 8 to 16, backend from Python 3.4 to 3.9, upgrading dependencies, introducing a better dependency management using Poetry and introducing better formatting/linting best practices.
         \\\textbf{Result:} Fresh working codebase with fewer bit rot.}
       \resumeItem{Surgery optimization program}
         {Rewriting a Java surgery scheduling program MVP using Optaplanner that was slow and could not easily fit hand-cooked scheduling heuristics in Rust.
         \\\textbf{Result:} Working program with DB in PostgreSQL, frontend in Vue2/JS, Backend in Python/Flask yet project got stopped because product was sold before in depth tests with different databases.}
    \resumeItemListEnd

    \resumeSubheading
      {Siléane}{Saint-Etienne, France}
      {Deep learning research engineer (internship)}{Apr 2022 - Oct 2022}
      \resumeItemListStart
        \resumeItem{AutoML tool for robotic applications based on ConvNets in Python}
          {Bibliographic research and implementation of state of the art bayesian optimization sampling and pruning algorithms to ensure fast convergence on continuous optimization problems with high cost per iteration.
         \\\textbf{Result:} Custom AutoML tool integrated to their Windows 10 software training models using XML specifications}
      \resumeItemListEnd

      \resumeSubheading
      {Kentika}{Lyon, France}
      {Data engineer on NLP (internship)}{May 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItem{NLP Python tool for text document databases}
          {Company's first step in the realm of AI, Development of a text recommandation and a Named Entity Recognition tool.
         \\\textbf{Result:} Pipeline to automatically process new data and generate text recommandations for each user with an anonymization of documents for law firm customers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Raytracing in Special Relativity}
      {Rust CLI tool capable of rendering (a 2D image) of a simple
      scene in a non-Euclidean 3D space. code on several CPUs. \href{https://github.com/Aboussejra/relativistic_ray_tracing}{Github-Link} }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Rust, Python, C/C++, TS, SQL, Bash, Latex}}
     \item{
     \textbf{Technologies}{: Linux, Git, Docker, Jenkins, AWS, Vue, Flask, FastApi, MySQL, PostgreSQL, Kedro, MLFlow, Pytorch, Pandas, Streamlit, Dash, Sklearn, Numpy}
     }
 \resumeSubHeadingListEnd

\section{Languages}
 \resumeSubHeadingListStart
   \item{
     \textbf{French}{: Mother tongue}}
     \item{
     \textbf{English}{: Proficient/Bilingual (TOEIC 950), oral and written.}
     }
     \item{
     \textbf{Spanish}{: Conversational, better oral skills than written due to lack of practice}
     }
 \resumeSubHeadingListEnd

\section{Hobbies}
\resumeSubHeadingListStart
\resumeSubItem{Powerlifting}
{Engaging in powerlifting as a hobby, old me was continuously striving to improve strength and performance in squat, bench press, and deadlift. New me just keeps up to shape.}
\resumeSubItem{Reading HackerNews}
{Passionate about staying up-to-date with the latest technology trends and industry news. Actively reading and engaging with the HackerNews community to gain insights into innovative technologies, programming languages, and emerging startups.}
\resumeSubItem{Tweaking Electronic Devices}
{Enjoying the process of tweaking electronic devices at home, software customization, and home automation. Constantly seeking ways to dodge ads and control software I am using.}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
